---
title: "aragonite_overlay_faster"
author: "Katherine Siegel"
date: "November 4, 2019"
output: html_document
---

## Description
Attempt to speed up aragonite_overlay for polygons by dividing raster into chunks before doing the extraction. 

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(raster)
library(sf)
# library(gdalUtils)
library(sp)
library(exactextractr)

### Pathways
coral_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/14_001_WCMC008_CoralReefs2018_v4/01_Data"
arag_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/Saturation"
eez_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/eez"

### Pathways on lab computer
coral_path_326 <- "E:/coral_acid/14_001_WCMC008_CoralReefs2018_v4/01_Data"
arag_path_326 <- "E:/coral_acid/Saturation"
```

## Coral map
Some of the coral locations are points, some are polygons. 

### Coral polygons
```{r}
### Open polygons and points files
c_poly <- st_read(file.path(coral_path_326,
                            "WCMC008_CoralReef2018_Py_v4.shp"))

# ### Calculate centroid of polygons
# c_poly$centroids <- st_centroid(c_poly$geometry)

### Reproject to match crs of aragonite rasters
c_poly <- st_transform(c_poly, 
                      crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

# ### Write out sf to rasterize in gdal
# st_write(c_poly, "coral_polygons.shp")

### Drop extra columns
c_poly <- c_poly %>%
  dplyr::select(., PARENT_ISO, ISO3, SUB_LOC, geometry)

### Add column for polygon ID
c_poly$poly_id <- 1:nrow(c_poly)

# ### Rasterize, with ISO3 as burn-in value. Use resolution of aragonite saturation layers (1.125, 0.4427083  (x, y))
# c_all_rast <- gdal_rasterize(src_datasource = c_all, 
#                              dst_filename = "c_all.tif",
#                              a = "ISO3",
#                              tr = c(1.125, 0.4427083))

```
## Aragonite projections
### Make raster stack
```{r}
### Get file names
arag_rast <- list.files(path = arag_path_326,
                        pattern = "^arg_.*tif$",
                        full.names = TRUE)

### Make stack
arag_stack <- raster::stack(arag_rast)

# ### Write out rasterstack (for use with polygons)
# writeRaster(arag_stack, filename = "arag_raster_stack.tif")
```

## Test exact extract
### exactextract on Brazil
```{r}
### Subset
bra_c <- subset(c_poly, ISO3 == "BRA")

### Extract one year
bra_c[, c(paste0("sum", "_", 
                 names(arag_stack[[1]])), 
          paste0("count", "_", 
                 names(arag_stack[[1]])))] <- exact_extract(arag_stack[[1]],
                                                           bra_c, c("sum", "count"))

### Write loop to extract each year
for (i in 1:nlayers(arag_stack)) {
  bra_c[, c(paste0("sum", "_", 
                 names(arag_stack[[i]])), 
          paste0("count", "_", 
                 names(arag_stack[[i]])))] <- exact_extract(arag_stack[[i]],
                                                           bra_c, c("sum", "count"))
  
}
```

## exactextract full data set 
started loop 10:27am, done 10:54am
```{r}
### Copy coral polygons df
coral_p <- c_poly

### Write loop to extract aragonite saturation state in each year
for (i in 1:nlayers(arag_stack)) {
  coral_p[, c(paste0("sum", "_", 
                     names(arag_stack[[i]])), 
              paste0("count", "_", 
                     names(arag_stack[[i]])))] <- exact_extract(arag_stack[[i]],
                                                                coral_p, 
                                                                c("sum", 
                                                                  "count"))
  
}

### Save output as csv
write_csv(coral_p, "polygon_aragonite_values.csv")
```


### Test extraction with Brazil
#### raster::extract
```{r}
### Convert to sp object
bra_sp <- as(bra_c, Class = "Spatial")

######### Get sum
### Extract sum aragonite saturation state (11:58am)
bra_vals_sum <- extract(arag_stack, bra_sp,
                              fun = 'sum', na.rm = TRUE,
                              sp = TRUE)

### Convert to sf 
bra_vals_sum <- st_as_sf(bra_vals_sum)
st_write(bra_vals_sum, "brazil_sum.shp")

######### Get count (1:12)
### Make masked raster
bra_mask <- mask(arag_stack[[1]], bra_sp)

### Set all values to 1
bra_mask <- 
bra_count <- cellStats(bra_mask, count)
bra_vals_count <- extract(arag_stack, bra_sp,
                              fun = function(x, ...) length(x),
                              sp = TRUE)
cellStats(bra_mask, range)

```

### Try with ISO3
```{r}
length(unique(c_poly$ISO3))

### Split by ISO3
c_split <- split(c_poly, c_poly$ISO3)
```

### Try with EEZs
Slow
```{r}
# ### Read in EEZ
# eez <- st_read(file.path(eez_path,
#                             "eez_v10.shp"))
# 
# ### Reproject to match crs of aragonite rasters
# eez <- st_transform(eez, 
#                       crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")
# 
# ### Intersect coral polygons with EEZs
# c_eez <- st_intersection(c_poly, eez)
```


## Extract values to coral polygons
Used Zonal Statistics as Table tool in ArcGIS to get SUM of raster values within polygons (grouped by ISO3)
```{r}
### Make subset of c_poly to try on
c_poly_ss <- subset(c_poly, poly_id > 5 & poly_id < 10)

### Convert to sp object
c_ss_sp <- as(c_poly_ss, Class = "Spatial")

### Extract for subset
poly_vals_ss <- extract(arag_stack, c_ss_sp,
                              fun = 'sum', na.rm = TRUE,
                              sp = TRUE)

### Convert to sf 
poly_vals_ss <- st_as_sf(poly_vals_ss)

##################################
### Run on full dataset
##################################
### Convert to sp object
c_sp <- as(c_poly, Class = "Spatial")

### Extract for subset
poly_vals_sum <- extract(arag_stack, c_sp,
                              fun = 'sum', na.rm = TRUE,
                              sp = TRUE)

### Convert to sf 
poly_vals_sum <- st_as_sf(poly_vals_sum)
```