---
title: "aragonite_overlay"
author: "Katherine Siegel"
date: "October 29, 2019"
output: html_document
---

## Description
Extract aragonite saturation state values for coral reefs. 

Data sources:  

* aragonite saturation state projections: Halley  
* coral reef locations: UNEP-WCMC, WorldFish Centre, WRI, TNC (2010). Global distribution of warm-water coral reefs, compiled from multiple sources including the Millennium Coral Reef Mapping Project. Version 4.0. Includes contributions from IMaRS-USF and IRD (2005), IMaRS-USF (2005) and Spalding et al. (2001). Cambridge (UK): UNEP World Conservation Monitoring Centre. URL: http://data.unep-wcmc.org/datasets/1  
* EEZs: Flanders Marine Institute (2018). Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10. Available online at http://www.marineregions.org/ https://doi.org/10.14284/312

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(raster)
library(sf)
library(gdalUtils)

### Pathways
coral_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/14_001_WCMC008_CoralReefs2018_v4/01_Data"
arag_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/Saturation"
# eez_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/eez"
```

## Coral map
```{r}
### Open polygons and points files
c_poly <- st_read(file.path(coral_path, "WCMC008_CoralReef2018_Py_v4.shp"))
c_pts <- st_read(file.path(coral_path, "WCMC008_CoralReef2018_Pt_v4.shp"))

### Drop extra columns from c_poly
c_poly <- c_poly %>%
  dplyr::select(., -Shape_Leng, -Shape_Area)

### Combine into single sf
c_all <- rbind(c_poly, c_pts)

### Reproject to match crs of aragonite rasters
c_all <- st_transform(c_all, 
                      crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"))
```

## Aragonite projections
```{r}
arag_2010 <- raster(file.path(arag_path, "arg_2010.tif"))
```

## Clip rasters 