---
title: "aragonite_overlay"
author: "Katherine Siegel"
date: "October 29, 2019"
output: html_document
---

## Description
Extract aragonite saturation state values for coral reefs. 

Data sources:  

* aragonite saturation state projections: Halley  
* coral reef locations: UNEP-WCMC, WorldFish Centre, WRI, TNC (2010). Global distribution of warm-water coral reefs, compiled from multiple sources including the Millennium Coral Reef Mapping Project. Version 4.0. Includes contributions from IMaRS-USF and IRD (2005), IMaRS-USF (2005) and Spalding et al. (2001). Cambridge (UK): UNEP World Conservation Monitoring Centre. URL: http://data.unep-wcmc.org/datasets/1  
* EEZs: Flanders Marine Institute (2018). Maritime Boundaries Geodatabase: Maritime Boundaries and Exclusive Economic Zones (200NM), version 10. Available online at http://www.marineregions.org/ https://doi.org/10.14284/312

## Set up
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### Load packages
library(tidyverse)
library(raster)
library(sf)
library(gdalUtils)

### Pathways
coral_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/14_001_WCMC008_CoralReefs2018_v4/01_Data"
arag_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/Saturation"
# eez_path <- "C:/Users/Katherine Siegel/Documents/Ren Edits/BP2_Tourism/eez"
```

## Coral map
Some of the coral locations are points, some are polygons. 

### Coral points
For the points, just need to extract aragonite raster value to points across time series. Steps:  

* reproject coral points to match aragonite raster  
* make raster stack and get values  
```{r}
### Open pt shp
c_pts <- st_read(file.path(coral_path, 
                           "WCMC008_CoralReef2018_Pt_v4.shp"))

### Reproject to match crs of aragonite rasters
c_pts <- st_transform(c_pts, 
                      crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Drop extra columns
c_pts <- c_pts %>%
  dplyr::select(., PARENT_ISO, ISO3, SUB_LOC, geometry)
```

### Coral polygons
```{r}
### Open polygons and points files
c_poly <- st_read(file.path(coral_path,
                            "WCMC008_CoralReef2018_Py_v4.shp"))

### Reproject to match crs of aragonite rasters
c_poly <- st_transform(c_poly, 
                      crs = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0")

### Write out sf to rasterize in gdal
st_write(c_poly, "coral_polygons.shp")

### Drop extra columns
c_poly <- c_poly %>%
  dplyr::select(., PARENT_ISO, ISO3, SUB_LOC, geometry)

### Add column for polygon ID
c_poly$poly_id <- 1:nrow(c_poly)

# ### Rasterize, with ISO3 as burn-in value. Use resolution of aragonite saturation layers (1.125, 0.4427083  (x, y))
# c_all_rast <- gdal_rasterize(src_datasource = c_all, 
#                              dst_filename = "c_all.tif",
#                              a = "ISO3",
#                              tr = c(1.125, 0.4427083))

```

## Aragonite projections
### Make raster stack
```{r}
### Get file names
arag_rast <- list.files(path = arag_path,
                        pattern = "^arg_.*tif$",
                        full.names = TRUE)

### Make stack
arag_stack <- raster::stack(arag_rast)

### Write out rasterstack (for use with polygons)
writeRaster(arag_stack, filename = "arag_raster_stack.tif")
```

### Extract values to coral points
```{r}
### Extract values
c_pts_arag <- cbind(c_pts, extract(arag_stack, c_pts))

### Save as csv
write_csv(c_pts_arag, "coral_points_arag.csv")
```

### Extract values to coral polygons
Used Zonal Statistics as Table tool in ArcGIS to get SUM of raster values within polygons (grouped by ISO3)
```{r}
### Make subset of c_poly to try on
c_poly_ss <- subset(c_poly, poly_id > 5 & poly_id < 10)

### Convert to sp object
c_ss_sp <- as(c_poly_ss, Class = "Spatial")

### Extract for subset
poly_vals_ss <- extract(arag_stack, c_ss_sp,
                              fun = 'sum', na.rm = TRUE,
                              sp = TRUE)

### Convert to sf 
poly_vals_ss <- st_as_sf(poly_vals_ss)

##################################
### Run on full dataset
##################################
### Convert to sp object
c_sp <- as(c_poly, Class = "Spatial")

### Extract for subset
poly_vals_sum <- extract(arag_stack, c_sp,
                              fun = 'sum', na.rm = TRUE,
                              sp = TRUE)

### Convert to sf 
poly_vals_sum <- st_as_sf(poly_vals_sum)
```


